Project Plan for a Time Series Visualization Framework

### 2016-04-28 docs/projectplan/projectplan.tex
Added timetable

\begin{table}[h!]
\centering
\begin{tabular}{|l|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Task}} & \textbf{Duration [h]} \\ \hline
\textbf{Research} &  \\ \hline
  - foo sub tasks & 42 \\ \hline
  - bar sub tasks & 42 \\ \hline
\textbf{Other Task} &  \\ \hline
  - foo sub tasks & 42 \\ \hline
  - bar sub tasks & 42 \\ \hline
\end{tabular}
\caption{Estimation for various sub tasks of the project.}
\label{tab:timetable}
\end{table}

@@

\begin{description}
 \item[Manuel Haid] foo
 \item[Thomas Mauerhofer] bar
 \item[Matthias Wölbitsch] baz
\end{description}

>>>>

\begin{table}[h!]
\centering
\begin{tabular}{|l|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Task}} & \textbf{Duration [h]} \\ \hline
\textbf{Research} &  \\ \hline
  - File import & 3 \\ \hline
  - APIs & 5 \\ \hline
  - Sockets & 10 \\ \hline
  - Python libraries & 5 \\ \hline
  - JavaScript visualization libraries & 5 \\ \hline
\textbf{Implementation} &  \\ \hline
  - User interface & 10 \\ \hline
  - Import model & 5 \\ \hline
  - Communication with APIs & 10 \\ \hline
  - Sockets & 15 \\ \hline
  - Generation of visualization primitives & 10 \\ \hline
  - Visualization & 15 \\ \hline
\textbf{Documentation} &  \\ \hline
  - Code & 2 \\ \hline
  - Projectplan & 10 \\ \hline
  - Report & 10 \\ \hline
\end{tabular}
\caption{Estimation for various sub tasks of the project.}
\label{tab:timetable}
\end{table}

@@

\begin{description}
 \item[Manuel Haid]: user interface, import model
 \item[Thomas Mauerhofer]: communication with APIs, visualization 
 \item[Matthias Wölbitsch]: generation of visualization primitives, sockets
\end{description}
